%\chapter*{ACKNOWLEDGMENT}
\begin{center}
{\bf ACKNOWLEDGMENT}\\[24pt]
\end{center}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENT}
{\baselineskip=1.5\baselineskip

I would like to express my gratitude to the following people and institutions which, in one way or another, greatly contributed towards the completion of this study. 

To my adviser \textbf{\textit{Engr. Jodie Rey D. Fernandez}} for painstakingly checking every detail of this paper. I am extremely thankful and indebted to you Sir for sharing your expertise and valuable guidance. Had not of your encouragement and moral support, this endeavor would surely fall to a complete obscurity.

To my panel members, \textbf{\textit{Engr. Mark Lister V. Nalupa}} and \textbf{\textit{Engr. Miriam M. Bergado}} for sharing your knowledge and diligently spending  your time in giving valuable insights, corrections and suggestions for the betterment of this study. I have high regards to both of you.

To the faculty and staff of the \textbf{\textit{Department of Computer Engineering}} for your encouragement and support.

To my classmates, \textbf{\textit{Methos}}, \textbf{\textit{Shirley}}, \textbf{\textit{Lovely}}, \textbf{\textit{Lady Lee}}, \textbf{\textit{Cris}}, and \textbf{\textit{Ma'am Bern}} for sharing your laughter and wonderful moments with me. Finally, sleepless nights and tiring days are over but they are all worth it.

To my friends, \textbf{\textit{Ruemar}}, \textbf{\textit{Chyn}}, \textbf{\textit{Vine}}, \textbf{\textit{Abigail}}, \textbf{\textit{Rachel}}, \textbf{\textit{Long}}, \textbf{\textit{Elaine}}, \textbf{\textit{Claire}}, \textbf{\textit{Allan}}, \textbf{\textit{Xander}}, \textbf{\textit{Laiza}}, \textbf{\textit{Ate Leslie}}, \textbf{\textit{Sir Greig}}, \textbf{\textit{Jean}}, \textbf{\textit{Sir Harold}}, \textbf{\textit{Ate Josh}}, \textbf{\textit{Ma'am Amelia}}, \textbf{\textit{Jovy}}, \textbf{\textit{Leonel}}, \textbf{\textit{Jerson}}, \textbf{\textit{Sir Raymund}}, \textbf{\textit{Sir Nur P.}}, \textbf{\textit{Mama Marge}}, \textbf{\textit{Mama Belle}}, \textbf{\textit{Mama Lady}}, \textbf{\textit{Mama Hazel}}, \textbf{\textit{Brother Mark}}, \textbf{\textit{Sir Nur}}, \textbf{\textit{Sir Elmer}} and to my \textbf{\textit{AHK Family}} for your prayers and moral support. You all made this journey worthy of remembering.

To my family, \textbf{\textit{Nanay Angga}}, \textbf{\textit{Papang Willy}}, \textbf{\textit{Nanay Toto}}, \textbf{\textit{Ina}}, \textbf{\textit{Ate Love}}, \textbf{\textit{Ate Ging}}, \textbf{\textit{Kuya Boboy}}, \textbf{\textit{Andi}}, \textbf{\textit{Marlo}} and \textbf{\textit{Ate Lyn}} for your unceasing love, moral and financial support. All of you are my inspirations which constantly remind me of not giving up amidst difficulties and uncertainties.

And to those people I failed to mention, who directly or indirectly, lent their hands, extended their prayers and support for the completion of this study. 

Above all, to our \textbf{\textit{Almighty God}}, whose unconditional love infinitely transcends all human comprehensions, provides us with good health, divine protection and bountiful blessings.

\begin{flushright}
\textbf{\textit{Jodie}}
\end{flushright}



}