\chapter{CONCLUSIONS AND RECOMMENDATIONS}
{\baselineskip=2\baselineskip

This chapter provides the summary of the results obtained in this study and gives some recommendations for further investigation.

\section{Summary of Findings}

The study’s findings address the initial research questions by confirming the effectiveness, reliability, and diverse applications of telemetry systems.
The "Summary of Findings" section provides a concise overview of the key results from your research. This section should be factual and focus on presenting the data without interpretation. It should include:

Key Results:

Briefly summarize the most significant findings.
Use bullet points or numbered lists for clarity if appropriate.
Present the data as it was found, highlighting major patterns, relationships, or trends.
Data Presentation:

Include tables, graphs, or charts that succinctly summarize the data.
Make sure each visual aid is clearly labeled and includes a brief description.
Coverage of Research Questions:

Address each of the research questions or hypotheses posed at the beginning of the study.
Summarize the results relevant to each question.

\section{Conclusion}
The "Conclusions" section interprets the findings and discusses their implications. This section should:

Interpret Findings:

Provide an interpretation of the data summarized in the previous section.
Discuss what the results mean in the context of the research questions or hypotheses.
Implications:

Explain the significance of the findings.
Discuss how the results contribute to the field of study or practical applications.
Limitations:

Acknowledge any limitations in the study that may affect the results or their interpretation.
%---------------------------------------------------------------------------------------------
\newpage
\section{Recommendations}

The "Recommendations" section provides actionable suggestions based on the study's findings and conclusions. This section should:

Practical Applications:

Offer specific recommendations for practitioners, policymakers, or other stakeholders based on the findings.
Future Research:

Suggest areas for further investigation that could address the study’s limitations or build on its findings.
Implementation:

Provide guidance on how the recommendations can be implemented effectively.
%---------------------------------------------------------------------------------------

}